### 2014-04-17 brains-protocol.tex
Add comments to choose figure for 4.

@@

\rk{comment results, transition to micro process}

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution.png}
    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 39).
    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
    After a period of time, each feature becomes concentrated in a specific range of its own.}
    \label{fig:timebags-evolution}
\end{figure*}

>>>>

\rk{Adapt this last paragraph once the model is really chosen (see below)}

@@

\rk{Choose which figure to show (see garbage at the end of file)}

\rk{Once chosen, comment results and transition to micro process}

%\begin{figure*}[!th]
%    \centering
%    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution.png}
%    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 39).
%    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
%    After a period of time, each feature becomes concentrated in a specific range of its own.}
%    \label{fig:timebags-evolution}
%\end{figure*}
